### 2024-02-05 docs/projects/noj/ggplot.qmd
Noj - rerendered

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ggplot_files/md-default0.js" type="text/javascript"></script><script src="ggplot_files/md-default1.js" type="text/javascript"></script>
<div style="max-height:600px;overflow-y:auto;"><table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table></div>

# Exploring ggplot

::: {.sourceClojure}
```clojure
(ns ggplot
  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]))
```
:::

@@

::: {.sourceClojure}
```clojure
(def plot
  (r "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point()
         + stat_smooth(method=\"lm\")
         + facet_wrap(~cyl))"))
```
:::

::: {.sourceClojure}
```clojure
(-> plot
    plotting/plot->svg
    kind/html)
```
:::

@@

<g id="surface6">

@@

::: {.sourceClojure}
```clojure
(-> plot
    r->clj
    (dissoc :data))
```
:::

::: {.printedClojure}
```clojure
{:layers [nil nil],
 :scales nil,
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
 :theme [],
 :coordinates nil,
 :facet nil,
 :plot_env nil,
 :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}

@@

Trying to mimic [cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list (WIP):

::: {.sourceClojure}
```clojure
(let [f (-> plot
            (r$ 'facet)
            (r$ 'params)
            (r$ 'facets))]
  (when (-> `(is.null ~f)
            r
            r->clj)
    (let [facet (-> `(ls ~f)
                    r
                    (r->clj)
                    first)]
      {:facet facet
       :facet-levels (-> plot
                         (r$ 'data)
                         (r/bra facet))})))
```
:::

::: {.printedClojure}
```clojure
{:facet "cyl", :facet-levels # A tibble: 234 × 1
     cyl
   &lt;int&gt;
 1     4
 2     4
 3     4
 4     4
 5     6
 6     6
 7     6
 8     4
 9     4
10     4
# ℹ 224 more rows
}

@@

<div style="background-color:grey;height:2px;width:100%;"></div>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main/projects/noj/notebooks/ggplot.clj">projects/noj/notebooks/ggplot.clj</a></small></small></pre></div>

>>>>

---
<style></style><style>.printedClojure .sourceCode {
  background-color: transparent;
  border-style: none;
}
</style>
<script src="ggplot_files/md-default4.js" type="text/javascript"></script><script src="ggplot_files/md-default5.js" type="text/javascript"></script><script src="ggplot_files/portal6.js" type="text/javascript"></script>

```{=html}
<table><tr><td>This is part of the Scicloj <a href="https://scicloj.github.io/clojure-data-scrapbook/">Clojure Data Scrapbook</a>.</td><a href="https://scicloj.github.io/clojure-data-scrapbook/"><img align="left" alt="SciCloj logo" src="https://scicloj.github.io/sci-cloj-logo-transparent.png" width="40" /></a></tr></table>
```

# Exploring ggplot
Here we explore [ggplot2](https://ggplot2.tidyverse.org/) from Clojure. The goal is to eventually implement a similar grammar in Clojure.

## Setup
We will use [ClojisR](https://scicloj.github.io/clojisr/) to call R from Clojure.

::: {.sourceClojure}
```clojure
(ns ggplot
  (:require [clojisr.v1.r :as r :refer [r r$ r->clj]]
            [clojisr.v1.applications.plotting :as plotting]
            [scicloj.kindly.v4.kind :as kind]
            [clojure.walk :as walk]
            [tablecloth.api :as tc]))
```
:::

@@

::: {.sourceClojure}
```clojure
(r/require-r '[base])
```
:::

::: {.printedClojure}
```clojure
nil

the base R library

## An example plot

::: {.sourceClojure}
```clojure
(-> "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point()
         + stat_smooth(method=\"lm\")
         + facet_wrap(~cyl))"
    r
    plotting/plot->svg
    kind/html)
```
:::

```{=html}

@@

<g id="surface929">

@@

```

## Representing plots as Clojure data
Inspired by
[cxplot](https://cxplot.com/index.html)'s internal ggplot.as.list finction, let us represent ggplot objects as R data structures.

::: {.sourceClojure}
```clojure
(defn ggolot->clj
  ([r-obj
    options]
   (ggolot->clj r-obj options []))
  ([r-obj
    {:as options
     :keys [avoid]}
    path]
   #_(prn path)
   (let [relevant-names (some->> r-obj
                                 r.base/names
                                 r->clj
                                 (filter (complement avoid)))]
     (cond
       ;;
       ;; a named list or a ggproto object
       (seq relevant-names) (->> relevant-names
                                 (map (fn [nam]
                                        [(keyword nam) (-> r-obj
                                                           (r$ nam)
                                                           (ggolot->clj options
                                                                        (conj path nam)))]))
                                 (into {}))
       ;;
       ;; a ggproto method
       (-> r-obj
           r.base/class
           r->clj
           first
           (= "ggproto_method"))
       :ggproto-method
       ;;
       ;; an unnamed list
       (-> r-obj
           r.base/is-list
           r->clj
           first)
       (-> r-obj
           r.base/length
           r->clj
           first
           range
           (->> (mapv (fn [i]
                        (prn [path (inc i)])
                        (-> r-obj
                            (r/brabra (inc i))
                            (ggolot->clj options
                                         (conj path [i])))))))
       ;;
       (r.base/is-atomic r-obj) (try (r->clj r-obj)
                                     (catch Exception e
                                       (-> r-obj println with-out-str)))
       :else r-obj))))
```
:::

For example:

::: {.sourceClojure}
```clojure
(-> "(ggplot(mpg, aes(cty, hwy))
         + geom_point())"
    r
    (ggolot->clj {:avoid #{"data" "plot_env"}}))
```
:::

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"]}}

@@

## Exlploring a few plots
Let us explore and compare a few plots this way:

::: {.sourceClojure}
```clojure
(defn h4 [title]
  (kind/hiccup [:h3 title]))
```
:::

::: {.sourceClojure}
```clojure
(defn ggplot-summary [r-code]
  (let [plot (r r-code)
        clj (-> plot
                (ggolot->clj {:avoid #{"data" "plot_env"}}))]
    (kind/fragment
     [(h4 "R code")
      (kind/md
       (format "\n```{r eval=FALSE}\n%s\n```\n"
               r-code))
      (h4 "plot")
      (-> plot
          plotting/plot->buffered-image)
      (h4 "clj data")
      (kind/pprint clj)
      (h4 "portal view")
      (->> clj
           (walk/postwalk (fn [form]
                            ;; Avoiding symbols that
                            (if (or (and (symbol? form)
                                         (-> form str (= "~")))
                                    (and (keyword? form)
                                         (-> form str (= "."))))
                              (str form)
                              form)))
           kind/portal)])))
```
:::

### A scatterplot

::: {.sourceClojure}
```clojure
(ggplot-summary
 "(ggplot(mpg, aes(cty, hwy))
         + geom_point())")
```
:::

```{=html}
<h3>R code</h3>
```

```{r eval=FALSE}
(ggplot(mpg, aes(cty, hwy))
         + geom_point())
```

```{=html}
<h3>plot</h3>
```

```{=html}
<img src="ggplot_files/0.png" style="width:100%;" />
```

```{=html}
<h3>clj data</h3>
```

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"]}}

@@

```{=html}
<h3>portal view</h3>
```

```{=html}
<div><script>portal_api.embed().renderOutputItem(
                {'mime': 'x-application/edn',
                 'text': (() => "^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :layers]] [^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :constructor]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector geom_point]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :position]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :inherit.aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :show.legend]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom_params]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :na.rm]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector false]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :aes_params]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stat]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :compute_layer]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :geom]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :non_missing_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"size\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"shape\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"colour\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_key]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default_aes]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shape]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 19.0]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :colour]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"black\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :size]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 1.5]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :fill]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :alpha]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :stroke]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector 0.5]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :required_aes]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"x\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"y\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :draw_panel]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}}], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :scales]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :mapping]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector cty]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"~\"]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector hwy]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :theme]] [], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :coordinates]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :expand]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :clip]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"on\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :limits]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector nil]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :default]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :facet]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :shrink]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector true]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :super]] ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :ggproto-method]]}, ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :labels]] ^{:source \"{}\", :line 58, :column 40, :end-line 58, :end-column 42} {^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :x]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"cty\"]]], ^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector :y]] [^#:portal.viewer{:default :portal.viewer/hiccup} [:div nil [:portal.viewer/inspector \"hwy\"]]]}}")}
                , document.currentScript.parentElement);</script></div>
```

### A scatterplot with colours

::: {.sourceClojure}
```clojure
(ggplot-summary
 "(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point())")
```
:::

```{=html}
<h3>R code</h3>
```

```{r eval=FALSE}
(ggplot(mpg, aes(cty, hwy, color=factor(cyl)))
         + geom_point())
```

```{=html}
<h3>plot</h3>
```

```{=html}
<img src="ggplot_files/1.png" style="width:100%;" />
```

```{=html}
<h3>clj data</h3>
```

::: {.printedClojure}
```clojure
{:layers
 [{:aes_params [],
   :stat {:compute_layer :ggproto-method, :super :ggproto-method},
   :show.legend [nil],
   :mapping nil,
   :super :ggproto-method,
   :inherit.aes [true],
   :geom_params {:na.rm [false]},
   :geom
   {:non_missing_aes ["size" "shape" "colour"],
    :draw_key :ggproto-method,
    :default_aes
    {:shape [19.0],
     :colour ["black"],
     :size [1.5],
     :fill [nil],
     :alpha [nil],
     :stroke [0.5]},
    :super :ggproto-method,
    :required_aes ["x" "y"],
    :draw_panel :ggproto-method},
   :stat_params {:na.rm [false]},
   :constructor [geom_point],
   :position
   {:compute_layer :ggproto-method, :super :ggproto-method}}],
 :scales {:scales [], :super :ggproto-method},
 :mapping {:x [~ cty], :y [~ hwy], :colour [~ [factor cyl]]},
 :theme [],
 :coordinates
 {:expand [true],
  :clip ["on"],
  :limits {:x nil, :y nil},
  :super :ggproto-method,
  :default [true]},
 :facet {:shrink [true], :super :ggproto-method},
 :labels {:x ["cty"], :y ["hwy"], :colour ["factor(cyl)"]}}

```{=html}
<h3>portal view</h3>
```

```{=html}
<div><script>portal_api.embed().renderOutputItem(
                {'mime': 'x-application/edn',

### 2024-02-05 docs/projects/noj/ml.qmd
Noj - rerendered

Residuals:
       Min          1Q      Median          3Q         Max
   -0.7904     -0.2163      0.0132      0.1774      0.8282

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           2.1092     0.2799     7.5344     0.0000 ***
sepal-width         0.5826     0.0743     7.8394     0.0000 ***
petal-length        0.7037     0.0624    11.2696     0.0000 ***
petal-width        -0.5557     0.1425    -3.8986     0.0002 ***
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3015 on 96 degrees of freedom
Multiple R-squared: 0.8707,    Adjusted R-squared: 0.8667
F-statistic: 215.5039 on 4 and 96 DF,  p-value: 1.668e-42

>>>>

Residuals:
       Min          1Q      Median          3Q         Max
   -0.8799     -0.2284      0.0138      0.2569      0.6354

Coefficients:
                  Estimate Std. Error    t value   Pr(>|t|)
Intercept           1.9687     0.3043     6.4705     0.0000 ***
sepal-width         0.6222     0.0800     7.7748     0.0000 ***
petal-length        0.6929     0.0713     9.7167     0.0000 ***
petal-width        -0.5072     0.1639    -3.0944     0.0026 **
---------------------------------------------------------------------
Significance codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 0.3196 on 96 degrees of freedom
Multiple R-squared: 0.8577,    Adjusted R-squared: 0.8533
F-statistic: 192.9066 on 4 and 96 DF,  p-value: 1.640e-40
